Path Model Temperature Comparisons

### 2016-10-31 path-temp-compare.Rmd
Add plot of total rainfall by year.

>>>>

```{r plot rainy season totals, echo=F}
library(ggplot2)
ggplot(rainy_season_ppt, aes(year, rain_v_total, group = year)) +
      geom_boxplot() +
      ylab("Rainfall (mm)") +
      xlab("Rainy Season Year") +
      ggtitle("Rainy Season Rainfall at Plots (nearest-neighbor assignment)") +
      theme_bw()
# ggsave("figures/rainy-season-ppt.png", dpi = 600)
```
